---
title: "Cristobal_FA9"
output: html_document
date: "2023-05-01"
---

1. An analogue signal received at a detector, measured in microvolts, is normally
distributed with mean of 200 and variance of 256.
(a) What is the probability that the signal will exceed 224 ğœ‡V?

```{r}
prob_more_224 <- pnorm(224, 200, sqrt(256), lower.tail = FALSE)
cat("Probability that signal is mopre than 224: ", prob_more_224)
```
(b) What is the probability that it will be between 186 and 224 ğœ‡V?
```{r}
p224 <- pnorm(224, 200, sqrt(256))
p186 <- pnorm(186, 200, sqrt(256))
cat("Probability that signal is mopre than 224: ", p224-p186)
```
(c) What is the micro voltage below which 25% of the signals will be?
```{r}
v_bel25 <- qnorm(.25, 200, sqrt(256))
cat("Micro voltage below which 25% of the signals is: ", v_bel25, "ğœ‡V.")
```
(d) What is the probability that the signal will be less than 240 ğœ‡V, given that
it is larger than 210 ğœ‡V?
```{r}
prob <- pnorm(240,200,sqrt(256))/(1-pnorm(210, 200, sqrt(256)))
cat("The probability is: ", prob)
```
(e) Estimate the interquartile range.
```{r}
interq_range <- qnorm(.75, 200, sqrt(256)) - qnorm(.25, 200, sqrt(256))
cat("The interquartile range is: ", interq_range)
```
(f) What is the probability that the signal will be less than 220 ğœ‡V, given that
it is larger than 210 ğœ‡V?
(g) If we know that a received signal is greater that 200 ğœ‡V, what is the probability that is in fact greater than 220 ğœ‡V?

2. A manufacturer of a particular type of computer system is interested in improving its customer support services. As a first step, its marketing department has
been charged with the responsibility of summarizing the extent of customer
problems in terms of system failures. Over a period of six months, customers
were surveyed and the amount of downtime (in minutes) due to system failures
they had experienced during the previous month was collected. The average
downtime was found to be 25 minutes and a variance of 144. If it can be
assumed that downtime is normally distributed:

(a) obtain bounds which will include 95% of the downtime of all the customers
```{r}
ub <- qnorm(.95, 25, sqrt(144))
lb <- qnorm(.05, 25, sqrt(144))
cat("Bounds are from",round(lb,2),"to",round(ub,2),".")
```
(b) obtain the bound above which 10% of the downtime is included.
```{r}
b_abv10 <- qnorm(.90, 25, sqrt(144))
cat("Bound is:",round(b_abv10,2))
```
